You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-26 paper/paper.tex
some more writing...

\section{Human Evaluation}
Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is innitially unclear how well the BLEU and PINC
automatic evaluation metrics perform when applied to evaluating paraphrases targeting a specific style of writing.  BLEU and PINC have previously
been shown to have high correlation with human judgements of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
previous work has evaluated automatically generated paraphrases which target a specific style of writing \cite{chen11}.

@@

\subsection{Maximum Entropy Style Metric}

\subsection{Evaluation}

>>>>

\section{Human Evaluation}
\label{human_evaluation}
Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is innitially unclear how well the BLEU and PINC
automatic evaluation metrics perform when applied to evaluating paraphrases targeting a specific style of writing.  BLEU and PINC have previously
been shown to have high correlation with human judgements of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
previous work has evaluated automatically generated paraphrases which target a specific style of writing \cite{chen11}.

@@

\subsection{Logistic Regression Style Metric}
We also consider a Logistic Regression based approach as an alternative to evaluating writing style.  The idea here, is to estimate the probability that each
sentence belongs to the target style, by using a large source and target training corpus to learn the parameters of a logistic regression model.
This probability is estimated as follows:
\[
%P(\text{style} = \text{target}|\text{output}) \propto \text{exp} \left( \vec{\theta} \cdot \vec{f(\text{output})} \right)
P(\text{style} = \text{target}|\text{sentence}) = \frac{1}{1 + e^{-\left( \vec{\theta} \cdot \vec{f(\text{sentence})} \right)}}
\]
Where $\vec{f(\text{sentence})}$ is a vector of ngrams, and $\vec{\theta}$ is a vector of weights.  
The parameters, $\vec{\theta}$, are optimized on the source and target corpus, where the assumption is that the target corpus
is in the target style, whereas the source corpus is not.\footnote{
  Parameters were optimized using MEGAM \url{http://www.cs.utah.edu/~hal/megam/}.
}

\subsection{Evaluation}
We trained both Logistic Regression and Cosine Similarity evaluation metrics using the original Shakespeare plays and modern translations as
the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficent between the automatic
evaluation metrics and human judgements reported in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|r|}
    \hline
    & & Pearson's $\rho$ \\
    \hline
    \hline
    semantic adequacy & BLEU & 0.35 \\
    \hline
    dissimilarity & PINC & 0.78 \\
    \hline
    style & BLEU & 0.07 \\
    \hline
    style & PINC & 0.20 \\
    \hline
    style & Cosine & 0.37 \\
    \hline
    style & Maximum Entropy & 0.47 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Correlation between various human judgements and automatic evaluation metrics}
  \label{correlation}
\end{table}

As can be seen in table \ref{correlation}, the correlation between semantic adequacy and BLEU appears smaller than that reported in previous work \cite{chen11}.  Presumably this is
due to the conflation of stylistic differences and semantic adequacy discussed discussed in section \ref{human_evaluation}, however the correlation between BLEU and human style
judgements seems too low to be of practical use.  PINC has very high correlation with judgments on dissimilarity, however we note that it is also highly correlated with human style
judgements.  To understand why PINC is highly correlated with human style judgements, notice that because the systems we are evaluating are targeting Shakesperean English, when changes
are made to the input they are likely to be in the target style.  Although PINC has high correlation with human judgements, it is likely not a useful measure of style in practice,
because for example a paraphrase system which makes many changes to the input, but targets a completely different style will also get a high PINC score.  
Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgements, with the Maximum Entropy score performing significantly better.
